---
title: "Clustering"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  gganimate = list(nframes = 50)
)

library(ggplot2)

theme_set(theme_minimal(base_size = 21))

if(require(showtext)){
 
  sysfonts::font_add_google("IBM Plex Sans", "plex")
  showtext::showtext_auto()
   
}
```

## Generating data set 

The main function is `sim_groups`, you need to define:

- A number of observations to draw.
- A number of groups. = = = 
- And set a seed if you want to replicate your results.

```{r setup}
library(klassets)

set.seed(123)

df <- sim_groups(n = 500, groups = 3)

plot(df)
```


## Apply cluster algorithms

### `stats::kmeans`

You can apply the `stats::kmeans` using `apply_statskmeans_clust`.

```{r}
dfc1 <- apply_statskmeans(df, centers = 2)

plot(dfc1)
```

### K-means: Basic {klassets} implementation

Or use a basic K-means implementation with:

```{r}
set.seed(234)

dfc2 <- apply_kmeans(df, centers = 2, max_iteration = 6)

plot(dfc2)
```

What is the benefit? In the second one use a helper function `kmeans_iterations`
to keep the iteration and see how the algorithm converges.

```{r}
set.seed(234)

kmi <- kmeans_iterations(df, centers = 2, max_iteration = 6)

plot(kmi)
```

Now we can use `gganimate` package using object result from `kmeans_iterations` 
due have the classification for every point in every step:

```{r}
kmi
```

So you can take the output of this function data and use `gganimate` to make the animation using in the `klassets` home page.  The code used in that animation can be found in the package using:

```{r}
system.file("animation_kmeans_iterations.R", package = "klassets")
```


