---
title: "Regression"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  gganimate = list(nframes = 50)
)

library(ggplot2)

theme_set(theme_minimal(base_size = 21))

if(require(showtext)){
 
  sysfonts::font_add_google("IBM Plex Sans", "plex")
  showtext::showtext_auto()
   
}
```

## Generating data set 

The main function is `sim_xy`, you need to define:

- A number of observations to simulate.
- Values $\beta_0$ and $\beta_1$.
- A distribution to sample $x$. For example `stats::runif` or  `purrr::partial(stats::rnorm, mean = 5, sd = 1)`.
- A function to sample error values like `purrr::partial(stats::rnorm, sd = 0.5)`.



```{r setup}
library(klassets)
library(ggplot2)
library(patchwork)

set.seed(123)

df_default <- sim_xy()

df_default

plot(df_default)

df <- sim_xy(n = 1000, x_dist = runif)

plot(df)
```

We can modify the data frame to get other types of relationships.

```{r}
df <- dplyr::mutate(df, y = y + 2*sin(5 * x))

plot(df)
```

## Apply classification algorithms

### Linear Regression

```{r}
df_lr <- apply_linear_model(df)

df_lr

plot(df_lr)
```

By default the model use `order = 1` of the variables, i.e, `response ~ x + y`. We can get a better fit if we increase the order. 

```{r}
df_lr2 <- apply_linear_model(df, order = 4, stepwise = TRUE)

attr(df_lr2, "model")

plot(df_lr2)
```

Testing various orders.

```{r}
orders <- c(1, 2, 3, 4)

orders |> 
  purrr::map(apply_linear_model, df = df) |> 
  purrr::map(plot) |> 
  purrr::reduce(`+`) +
  patchwork::plot_layout(guides = "collect") &
  theme_void() + theme(legend.position = "none")
```

### Regression Tree `partykit::ctree`

```{r}
df_rt <- apply_regression_tree(df, maxdepth = 2)

plot(df_rt)

plot(attr(df_rt, "model"))

plot(apply_regression_tree(df))
```


### Linear Model Tree `partykit::mltree`


```{r}
df_lmt <- apply_linear_model_tree(df, maxdepth = 3)

plot(df_lmt)

plot(attr(df_lmt, "model"))

plot(apply_linear_model_tree(df))
```


